Classification and characterization of anthropogenic plant communities at the ecoregion level

### 2024-06-12 doc/title-page.Rmd
Zenodo link ⛓️

Original datasets, R code for analysis and Rmarkdown code for creation of the manuscript can be accessed at the GitHub repository <https://github.com/efernandezpascual/anthropogenic>. Upon publication, a version of record of the repository will be deposited in Zenodo.

>>>>

Original datasets, R code for analysis and Rmarkdown code for creation of the manuscript can be accessed at the GitHub repository <https://github.com/efernandezpascual/anthropogenic> stored at https://zenodo.org/doi/10.5281/zenodo.11613571.

. Upon publication, a version of record of the repository will be deposited in Zenodo.
